Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
Add acknowledgements

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test
% Speak about the complexity and parallelization of the methods

>>>>

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test
% Speak about the complexity and parallelization of the methods
\begin{scriptsize}
\paragraph{Acknowledgements.} A. Joly and G. Louppes are research
fellows of the FNRS, Belgium.  A. Sutera is supported by a F.R.I.A. scholarship.
This work is supported by PASCAL2 and the IUAP
DYSCO, initiated by the Belgian State, Science Policy Office.
Computational ressources have been provided by the Consortium des Équipements
de Calcul Intensif (CÉCI), funded by the Fonds de la Recherche Scientifique de
Belgique (F.R.S.-FNRS) under Grant No. 2.5020.11
\end{scriptsize}
